Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-12 doc/report/msc-report.tex
Introduction: added Problem description, Goal and Scope.

@@

% TODO: fixa cites. Luckily, this is a problem that has already been solved.
Google has published papers on the MapReduce framework \cite{mapreduce}, which
allows for parallel processing of large data sets, and The Google File System
\cite{gfs}, a scalable, distributed file system. The Apache Hadoop
\cite{hadoop} project has published free software implementations of a
MapReduce framework and a distributed file system, both of which build on the
ideas in the papers published by Google.

\section{Problem description}

Last.fm

SQL

EXPLODE

\section{Scope}

Time-series based analysis is the most important one when analysing web
logs, it comes natural since all log entries are timestamped.
\cite{discoveringweb} It is also the most common form we have seen for logs
in general.

Assuming that time-series analysis is the most important, we have imposed
the restriction on the system that is built so that it only handles
time-series. Because of this restriction the data store obviously becomes
less general purpose. Although since most log data is time-series based
this restriction does not cripple the system much---if at all.

\subsubsection*{Related work}

@@

\section{Goal}

The goal (sv. syfte) with our work.

>>>>

\section{Background}

@@

Luckily, this is a problem that has already been solved. Google has published
papers on the MapReduce framework \cite{mapreduce}, which allows for parallel
processing of large data sets, and The Google File System \cite{gfs}, a
scalable, distributed file system. The Apache Hadoop \cite{hadoop} project has
published free software implementations of a MapReduce framework and a
distributed file system, both of which build on the ideas in the papers
published by Google.

\section{Problem description}
% Problemsbeskrivning.

At last.fm there is a central repository where metrics and statistics for
various services are stored. There is a web site for internal use that
displays graphs of the services and their statistics. Examples of statistics
are web site usage broken down by country, scrobbling broken down by client
and daily subscription counts.

The statistics are stored in a relational database. Each measure is stored
atomically; a summing operation across numerous rows is required to answer
queries. The database is bursting at the seams because of the size of the
data. Some of the problems with the current setup is that adding a new data
source to the database requires manual intervention and that some of the
questions that analysts ask can not be answered in real-time.

Last.fm foresees that its data sets will continue to grow and would like to
move away from the current setup towards a scalable data store. The data store
should be able to answers most questions in real time. It should be easy
to publish new data sets.

\section{Goal}
% Syftesformulering.

The goal is to build a tool that enables its users to easily turn log files
into aggregates. The tool should provide a simple mechanism for data analysis
(import) and querying (export).

The data analysis will require the user to write a MapReduce map. The queries
will be performed via an export API for consumption by computer programs.

The queries will always be made over a time range and for a single unit. The
tool will support analytical functions such as drill-down, slicing, etc.

The tool should be aware of dimensions in general and the dimension of time in
particular. Measurements will be specified in a unit. There will be no limit
on the number of units.

There should be no theoretical boundary on the number of dimensions. Common
queries must be answered expediently to allow for analysts to explore data in
real time.

\section{Scope}
% Avgransning.

The data store is just that: a data store with import and export
functionality. The data store does not interpret the data it store.

The data store is time-series-based: all data must include the time dimension.

All measures are integers. Sum is the only supported aggregation function. The
data store does not support reach-like data (i.e. number of unique visitors)
since it is not summable.

There is no functionality for plotting data sets, etc.

\section{Related work}

@@
